---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# RcppGLM

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

`RcppGLM` implements the GLM fitting algorithm in c++ using Armadillo. It follows the code from [1]. Requires c++11 at the moment.

It is work in progress and mainly for learning purposes.

There are some numerical problems depending on the input. But a lot of stuff seems to work already.

## Supported families and link functions

* Gaussian (`gaussian_family`) (log, identity, inverse (fails at the moment `¯\_(ツ)_/¯`️))
* Poisson (`poisson_family`) (log, sqrt, identity)
* Binomial (`binomial_family`) (logit, probit)

## Example

Logistic regression:

```{r example1}
library(RcppGLM)
X <- model.matrix(I(mpg < 20) ~ -1 + hp + drat + cyl, data = mtcars)
y <- mtcars$mpg < 20
family <- binomial_family(link = "logit")
glm_fit(X, y, family)
```

Same as the R implementation:

```{r}
coef(glm.fit(X, y, family = stats::binomial(link = "logit")))
```

Poisson regression:

```{r example2}
X <- model.matrix(hp ~ -1 + drat + cyl, data = mtcars)
y <- mtcars$hp
family <- poisson_family(link = "log")
glm_fit(X, y, family)
```

Same as the R implementation:

```{r}
coef(glm.fit(X, y, family = stats::poisson(link = "log")))
```

## References

1: Arnold, T., Kane, M., & Lewis, B. W. (2019). A Computational Approach to Statistical Learning. CRC Press.

